Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-16 robdml.tex
tex

\textbf{Adversarial Defense.}
%
To battle against the attacks, some defenses incur gradient masking
effect, but often lead to a false sense of security~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} is compromised in~\cite{cw}.
%
It has been shown that ensemble of weak defenses is not robust~\cite{ensembleweak}.
%
Other defenses are also proposed, such as input
preprocessing~\cite{deflecting}, or a randomization inside the
network~\cite{self-ensemble}.
%
But many defenses are still susceptible to adaptive attacks~\cite{adaptive}.
%
Of all defenses, adversarial training remains to be one of the most effective
methods~\cite{bilateral,advtrain-triplet,benchmarking}, consistently showing
promising empirical robustness, although suffers from high training
cost and performance drop on benign examples~\cite{odds}.

>>>>

\textbf{Adversarial Defense.}
%
Various defenses are proposed to counter the attacks.
%
However, defenses incurring gradient masking
lead to a false sense of robustness~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} is compromised in~\cite{cw}.
%
Ensemble of weak defenses is not
robust~\cite{ensembleweak}.
%
Other defenses such as input
preprocessing~\cite{deflecting}, or a randomization~\cite{self-ensemble} are proposed.
%
But many of them are still susceptible to adaptive attacks~\cite{adaptive}.
%
Of all defenses, adversarial training~\cite{madry} consistently remains to be one of the
most effective
methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,weightperturb,featurescatter},
but suffers from high training cost~\cite{freeat,fastat,yopo}, performance drop on
benign examples~\cite{odds,geometry,onmanifold}, and overfitting on adversarial examples~\cite{bagoftricks,overfitting}.
